---
title: "Deep Learning notes"
author: "Kurt"
date: "2023-09-05"
output: 
  html_document: 
    keep_md: yes
---


## Loading data options
```{r setup, eval=TRUE, echo=FALSE}
library(tensorflow)
library(keras)
mnist <- dataset_mnist()
```

####  unadvised
```{r unadvised_load, eval=FALSE}
# train_images <- mnist$train$x
# train_labels <- mnist$train$y
# test_images <- mnist$test$x
# test_labels <- mnist$test$y
```

#### Preferred
```{r preferred_load, eval=TRUE}
c(c(train_images, train_labels), c(test_images, test_labels)) %<-% mnist

```

#### Data structure

```{r train-str}
str(train_images)
str(train_labels)

```
```{r test-str}
str(test_images)
str(test_labels)

```
#### Network architecture
The model consists of a sequence of two dense, fully connected, neural layers.
The second layer is a 10-way softmax classification layer, which returns an 
array of 10 probability scores, which sum to one. Each score is the probability 
the current digit image belongs to one of the 10 digit classes.
```{r model}
model <- keras_model_sequential(list(
  layer_dense(units = 512, activation = "relu"),
  layer_dense(units = 10, activation = "softmax")
))
```
#### Compilation step
To train, the model needs an optimizer, a loss function and metrics.
* The optimizer is how the model updates itself to improve performance.
* The loss function measures performance on the training data.
* Metrics measure and monitor the accuracy of the performance.

```{r compile}
compile(model,
        optimizer = "rmsprop",
        loss = "sparse_categorical_crossentropy",
        metrics = "accuracy")
```

#### Reshape the data
From 60k different 28 by 28 pixel images as matrices, with a range of integer 
values in [0, 255], to 60k vectors length 784, which is 28 * 28, with scaled 
with double values in [0, 1].
```{r reshape}
train_images <- array_reshape(train_images, c(60000, 28 * 28))
train_images <- train_images / 255
test_images <- array_reshape(test_images, c(10000, 28 * 28))
test_images <- test_images / 255
```

#### Fit the model

```{r fit}
fit(model, train_images, train_labels, epochs = 5, batch_size = 128)

```
Results look overfitted after second epoch. The loss increases and the acuracy deteriorates.

#### Prediction with the model
Make predictions with test data
```{r predict}
test_digits <- test_images[1:10, ]
predictions <- predict(model, test_digits)
str(predictions)
predictions[1, ]
test_labels[1]
```
The 0.982 is in the 8th place of the probability output vector. 
The digits start at zero, so it predicts 7.

#### Evaluate the model
Check the accuracy
```{r metrics}
metrics <- evaluate(model, test_images, test_labels)
        metrics["accuracy"]
```
89.89% for this run. 
